Summary Tables

### 2019-04-09 summary_tables.Rmd
Add summarytools as examples, and add some desc

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment=NA, prompt=FALSE, cache=FALSE, echo=TRUE, results='asis')

@@

```{r loadLibraries, echo = F}
library(summarytools)
library(knitr)
library(summarytools)
#library(tidyverse)

@@

@@

```{r trip_tables = "asis"}

for(city in cities){
    td <- io[[city]]$dist
    print(kable(td, caption = paste("Distance table for ", city)))
    cat("\n")
}

for(city in cities){
    td <- io[[city]]$dur
    print(kable(td, caption = paste("Duration table for ", city)))
    cat("\n")
}

@@

```{r pa = "asis"}

for (city in cities){
  td <- io[[city]]$outcomes$mmets
  print(dfSummary(td))
  cat("\n")

}

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment=NA, prompt=FALSE, cache=FALSE, echo=F, results='asis')

@@

```{r loadLibraries, echo = F, message = F}
suppressWarnings({

library(summarytools)
library(knitr)
library(summarytools)
library(dplyr)
})

@@

# Set plot_mmets to F
plot_mmets <- F

@@

## Scenario definition
Table displays highest propensity for each distance category, for a given mode.

```{r scen_prop = "asis"}

scen_prop <- round(io$scen_prop, 2)

rownames(scen_prop) <- paste(rownames(io$scen_prop), "scen", sep = "_")

kable(scen_prop, headings = "Scenario Proportions")

@@

## Distance tables
Case study specific distance tables for baseline and five scenarios

```{r trip_dist = "asis"}

for(city in cities){
    td <- io[[city]]$dist %>% mutate_if(is.numeric, round, digits = 2)
    colnames(td)[3:7] <- rownames(scen_prop)
    print(kable(td, caption = paste("Distance table for ", city)))
    cat("\n")
}

@@

## Distance tables
Case study specific duration tables for baseline and five scenarios

```{r trip_dur = "asis"}

for(city in cities){
    td <- io[[city]]$dur %>% mutate_if(is.numeric, round, digits = 2)
    colnames(td)[3:7] <- rownames(scen_prop)
    print(kable(td, caption = paste("Duration table for ", city)))
    cat("\n")
}

```{r pa, echo = F, message = F}

if (plot_mmets){

  dfSummary(accra_mmets <- io[["accra"]]$outcomes$mmets, style = 'grid', graph.magnif = 0.75, tmp.img.dir = "/tmp")

  dfSummary(sao_paulo_mmets <- io[["sao_paulo"]]$outcomes$mmets, style = 'grid', graph.magnif = 0.75, tmp.img.dir = "/tmp")

  dfSummary(delhi_mmets <- io[["delhi"]]$outcomes$mmets, style = 'grid', graph.magnif = 0.75, tmp.img.dir = "/tmp")

  dfSummary(bangalore_mmets <- io[["bangalore"]]$outcomes$mmets, style = 'grid', graph.magnif = 0.75, tmp.img.dir = "/tmp")
}
